%Resume.tex
%disable chktex warnings
% chktex-file 1
%-------------------------
% Resume in Latex
% Original Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom{}
\raggedright{}
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-15pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule{} \vspace{-8pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}
}
\newcommand{\resumeSubheadingContinue}[2]{
  \vspace{-1pt}
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textit{\small #1} & \textit{\small #2} \\
    \end{tabular*}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\vspace{1pt}\begin{itemize}[noitemsep,nolistsep,leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[noitemsep,nolistsep]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  %\textbf{\href{http://pcwilcox.com/}{\Large Pete Wilcox}} & Email :
    \textbf{{\Large Austen Barker}} & +1 (650) 575\textendash{}7253  \\
	\href{mailto:austenbarker@yahoo.com}{austenbarker@yahoo.com},\href{mailto:atbarker@ucsc.edu}{atbarker@ucsc.edu}
  %\href{http://pcwilcox.com/}{http://www.pcwilcox.com} & Mobile : +1-510-393-4074 \\
    & github/LinkedIn: atbarker
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, Santa Cruz}{Santa Cruz, CA}
      {Doctor of Philosophy in Computer Science}{September 2018 \textemdash{} Present}
      \resumeItemListStart
        \resumeItem{Dissertation}
	  {\emph{Artifice: Rethinking the Adversary to Design Usable Deniable Storage}}
      \resumeItemListEnd

    \resumeSubheading
      {University of California, Santa Cruz}{Santa Cruz, CA}
      {Master of Science in Computer Science}{September 2017 \textemdash{} June 2018}
      \resumeItemListStart
        \resumeItem{Masters Project}
	  {\emph{Artifice: A Deniable Steganographic File System}}
      \resumeItemListEnd

    \resumeSubheading
      {University of California, Santa Cruz}{Santa Cruz, CA}
      {Bachelor of Science in Computer Science;  GPA:\@ 3.60}{September 2013 \textemdash{} June 2017}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, Santa Cruz}{Santa Cruz, CA}
      {Graduate Student Researcher}{April 2018 \textemdash{} Present}
      \resumeItemListStart
        \resumeItem{\href{https://www.ssrc.ucsc.edu/proj/Artifice.html}{Artifice}}
	  {Ongoing research into deniable storage systems. Designed and built a deniable block device driver for the Linux kernel. Red team forensic analysis and evalation of deniable storage systems.} 
	\resumeItem{\href{https://www.ssrc.ucsc.edu/proj/securefs.html}{Lethe}}
	  {Efficient secure deletion system for use with file systems or key value stores. Provably deletes encrypted data by efficient key revocation.}
      \resumeItemListEnd

    \resumeSubheading
      {University of California, Santa Cruz}{Santa Cruz, CA}
      {Teaching Assistant}{September 2019 \textemdash{} December 2019, January 2018 \textemdash{} March 2018}
      \resumeItemListStart
        \resumeItem{CSE-13S}
          {Computer Systems and C Programming, Fall quarter 2019}
        \resumeItem{CMPS-111}
          {Introduction to Operating Systems, Spring quarter 2018}
      \resumeItemListEnd

    \resumeSubheading
      {DataStax}{Santa Clara, CA}
      {Information Security Intern}{July 2017 \textemdash{} December 2017, June 2018 \textemdash{} September 2018}
      \resumeItemListStart
        \resumeItem{Single Sign-on API}
	  {Designed and implemented a single sign-on authentication API, user database, and password handling utilities in Go for a SAAS database platform.}
        \resumeItem{Deployment Setup and Hardening Automation}
          {Wrote setup and server hardening automation scripts for a distributed database system using Chef, Vagrant, and Docker.}
      \resumeItemListEnd

    \resumeSubheading
      {TidalScale}{Los Gatos, CA}
      {Software Engineer Intern}{June 2016 \textemdash{} September 2016}
      \resumeItemListStart
        \resumeItem{TS-stats}
          {Python administration and monitoring utility for a distributed hypervisor. Collected metrics from multiple machines in a distributed system, stored them in a small time series database, and displayed using an ncurses GUI.}
        \resumeItem{Ubuntu Server Certification}
	  {Performed testing on a distributed hypervisor platform for the Ubuntu Server Certification process. Worked with kernel developers to identify and solve issues uncovered by the certification tests.}
      \resumeItemListEnd

    \resumeSubheading
      {Immediate Insight}{Los Altos, CA}
      {Intern}{June 2014 \textemdash{} September 2014, June 2015 \textemdash{} September 2015}
      \resumeItemListStart
        \resumeItem{Kaiser Permanente Deployment}
	  {Supported the deployment of a IT data analytics tool within the Kaiser Permanente IT infrastructure.}
        \resumeItem{Product Testing}
          {Installation, capacity, reliability, and operational testing of an IT data analytics platform.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Artifice, Deniable Storag System}
      {Deniable steganographic storage system written as a devicemapper virtual block device kernel module. Utilizes Shamir Secret Sharing, Reed-Solomon erasure codes, and encryption techniques to provide obfuscation and redundancy for hidden data. Further work done on red team testing and forensic analysis of the system to verify the security of Artifice's design and implementation. Code primarily written in C with testing scripts in Python.}
    \resumeSubItem{Lethe, Efficient Secure Deletion}
      {Key derivation and encryption system that enables secure deletion of encrypted data by efficiently revoking a key through the use of keyed hash trees. Current implementation written in C/C++.}
    \resumeSubItem{Vinz Clortho}
      {Covert timing channel implemented as a netfilter Linux kernel module for the secure exfiltration of encryption keys from a distributed system relying on a gossip protocol.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}
      {C, C++, Python, Go, Java, Lisp/Scheme}
    \resumeSubItem{Technologies}
      {FreeBSD, Linux, Windows, Git, Docker}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}

